---
title: "ley Kimteng"
output: html_notebook
---

1. Write a R code to Generate 6X6 matrix (A) using the random numbers between 1 to 100 generate another 6x6 matrix (B) using random numbers between 500 to 600.
```{r}
## create A and B
x <- sample(1:100)
y <- sample(500:600)
A <- matrix(x, nrow = 6, ncol = 6)
B <- matrix(y, nrow = 6, ncol = 6)
A
B

# a. Find the range of matrices A and B.
print("range of matric A")
range(A)
print("range of matric B")
range(B)

# b.Find the max value from each row of the matrices A and B.
print("The max value from each row of the matrices A")
apply(A,1,max)
print("The max value from each row of the matrices B")
apply(B,1,max)

# c. Find the diagonal values of matrices A&B.
print("The diagonal values of matrices A&B")
z <- A / B
diag(t(z))

# d. Multiply matrices A and B
print("Multiply matrices A and B (inner product)")
A %*% B
# e. Replace the 4th row of Matrix A with diagonal values of matrix B
print("Replace the 4th row of Matrix A with diagonal values of matrix B")
A[4, ] <- diag(t(B))
A
# f. Multiply matrices A & B and store the values on X.
print("Multiply matrices A & B and store the values on X")
X <- A %*% B
X
# g. Divide the matrix A with matrix B.
print("Divide the matrix A with matrix B")
A / B

```


2. Create a table using dataframe/tibble with the following categories(a to f) (10 marks)
```{r}
fn<-c("Kimmonyvorn","Nataly","Kimteng","Dara","Menghong","Bongrong","Jenny","Lynan","Leapheng","Sothea")
ln<-c("Chea","Chea","Ley","Kruy","Chhor","Kit","Sun","Thon","Ty","Youk")
ag<-c(20,19,20,21,22,19,20,20,20,19)
oc<-c("Doctor","Student","Teacher","Student","Doctor","Teacher","Student","Doctor","Student","Teacher")
pl<-c("Phnom Penh","Siem Reap","Kampong Cham","Siem Reap","Kampong Cham","Phnom Penh","Phnom Penh","Kampong Cham","Phnom Penh","Siem Reap")
rn<-sample(1:10,10)
tabledata<-data.frame(FirstName=fn,LastName=ln,Age=ag,Occupation=oc,Place=pl,RandomNumber=rn)
tabledata
```

3. Create a .txt file (Minimum : 150 words) with the latest news (In English) in cambodia from
the official news agency’s website(Note: Include the reference link) and do the following
```{r}
library(tokenizers)
#a. Read the .txt file
# text from url: https://www.phnompenhpost.com/national/mekong-levels-set-drop-during-power-grid-work
data <- read.delim("/Users/kimteng/Documents/Semester 7/Data science/news.txt")
data

#b. Perform the Tokenization count the words
words_data <- paste0(data)
tokens <- tokenize_words(words_data)
count <- count_words(words_data)
count

#c. Identify the most repeated word and replace that word with “KIT”
#Identify the most repeated word
most_words <- names(table(tokens))[as.vector(table(tokens))==max(table(tokens))]
most_words_count <- max(table(tokens))
print("The Most repeated word is: ")
most_words
print("repeated for:  ")
most_words_count

#replace that word with “KIT”
subs <- gsub(most_words, "KIT", words_data)
subs

#d. Perform the Sentiment analysis
library(sentimentr)
# To display the sentences
result1<- get_sentences(subs) 
result1

#number of sentences and words(Sentiment at the sentence level)
result2<- sentiment(subs) # To know 
result2

# Aggregated sentiment group by each sentiment
result3 <-sentiment_by(subs) 
result3

# Emotion at the sentence level one by one
result4<- emotion(subs) 
result4

# Aggregated emotion group by emotion
result5<- emotion_by(subs) 
result5

# Profanity at the sentence level
result6<- profanity(subs) 
result6

# Aggregated profanity by group(s)
result7<- profanity_by(subs) 
result7

#e. Plot the graph between “words count” and “words” using geom_col()
#e.1. X-axis title =“Number of words”, Size=10, Bold, Text in Blue color, Center, space between graph and title = 20.
#e.2. Y-axis title =“List of words”, Size=10, Bold, Text in Red color, Center, space between graph and title = 20.
#e.3. Graph title =”Text Mining using R”,Size = 25, Bold, Center, Text in Yellow color, space between graph and title = 25.
library(tidytext)
table(tokens)
# create table
dataset <- data.frame( text=words_data)
dataset
dataset <- dataset %>% unnest_tokens(word, text)  

#plot the graph
plot <- dataset %>%  count(word) %>% ggplot(aes(n, word())) + geom_col() 
plot + ggtitle("Number of words")+
  xlab("Text Mining using R") +
  ylab("List of words") + theme(
  axis.title.x=element_text(size=10, color="blue", face="bold", margin=margin(t=20,r=20,b=0,l=0)),
  axis.title.y=element_text(size=10, color="red", face="bold", margin=margin(t=0,r=20,b=0,l=20)),
  plot.title=element_text(size=25, color="yellow", face="bold", margin=margin(t=25,r=0,b=25,l=0))
  )

```


4. Find the assigned Dataset from the list below and perform the following (20 Marks)
```{r}
# a. Import and Clean the dataset.
library("tidyverse")
dataset <- read_csv("/Users/kimteng/Documents/Semester 7/Data science/early-senate-polls.csv")
dataset
#is.na(dataset)
# the dataset is already clean there is no NA so no need to clean again.

# b. Find the x and y variables(axis) from the assigned dataset and give the reason for
# selecting Election_result as X and Year as Y because it would be easy to view year in Y axis. If we do this we can view each year in the column graph that easy to understand.
plot <- ggplot(dataset, aes(x=election_result, y=year)) + 
    xlab("Election Result") +
    ylab("Election Year")

# c. Plot the graph using geom_col() and perform the linear model in statistics.
# using geom_col
plot <- plot+geom_col()

#perform linear model in smooting
plot <- plot+geom_smooth(method="lm")
plot

# d. Perform the facet with the available columns(Choose the any two variables from the columns)
# use facet with 2 variable by the year of election and presidential_approval
plot+facet_grid(presidential_approval~year)

# use facet with 1 variable by the year of election
plot <- plot+facet_wrap(~year)
plot
# because it diffcult to view 2 variable so choose only 1 variable

# e. Use the theme layer to do the following (Note: Based on dataset, name the x and y axis graph)
#e.1. x-axis title =“________”, Size=10, Bold, Text in Green color, Center, space between graph and title = 20.
#e.2. y-axis title =“________”, Size=10, Bold, Text in Yellow color, Center, space between graph and title = 20.
#e.3. Graph title =”_________”,Size = 25, Bold, Center, Text in Blue color, space between graph and title = 25.
plot <- plot +
  ggtitle("Election Result") + theme(
  axis.title.x=element_text(size=10, color="green", face="bold", margin=margin(t=20,r=20,b=0,l=0)),
  axis.title.y=element_text(size=10, color="yellow", face="bold", margin=margin(t=0,r=20,b=0,l=20)),
  plot.title=element_text(size=25, color="blue", face="bold", margin=margin(t=25,r=0,b=25,l=0))
  )
plot

#save file
ggsave(filename="leykimteng.png", units="cm", width=25, height=25)
```

